NFC and burnout in teachers - A replication and extension study

### 2021-09-13 Manuscript/Manuscript.Rmd
changed correlation table to also display DRRs

    # create a vector of consistencies to be used as the diagonal in a table later
    consist_diag <- cbind(format(round(t(consistencies[2,2:11]), digits = 2), nsmall = 2), rep("(",10),
                          format(round(t(consistencies[5,2:11]), digits = 2), nsmall = 2), rep(")",10))
    # paste together to create the output "alpha(omega)"
    consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")

@@

    # correlate variables, including the demand resource ratios
    corr_with_drr <- correlation_matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                                    "scs","ncs","dth","dtl","drf","covb")],
                                       type = "spearman",
                                       use = "lower",
                                       replace_diagonal = TRUE,
                                       replacement = "")

    # correlate variables without demand resource ratios (for table in manuscript)
    corr_no_drr <- correlation_matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                                    "scs","ncs","covb")],
                                       type = "spearman",
                                       use = "lower",
                                       show_significance = FALSE,
                                       replace_diagonal = TRUE,
                                       replacement = "")

    # add previously assembled diagonal with alpha and omega values
    diag(corr_no_drr) <- consist_diag

    # set row and column names for better table printing
    row.names(corr_no_drr) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","COV")
    colnames(corr_no_drr) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","COV")

    # create array with p-values of correlation coefficients
    corr_pvalues <- rcorr(as.matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                        "scs","ncs","covb")]), type = "spearman")$P
    # replace upper triangle with NA
    corr_pvalues[upper.tri(corr_pvalues, diag = TRUE)] <- NA

@@

    # convert to matrix for the paste()-function
    corr_no_drr <- as.matrix(corr_no_drr)
    corr_pvalues <- as.matrix(corr_pvalues)

    # paste correlations and asterisks together
    correlations <- matrix(paste(corr_no_drr, corr_pvalues, sep = ""),
                           nrow = nrow(corr_no_drr), dimnames = dimnames(corr_no_drr))

@@

@@

  desc_table <-
  kbl(correlations,
      booktabs = T, # no vertical lines
      escape = F, # correctly print special characters
      align = rep("l",11)) %>% # right aligns the text in every column except for the first
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, COV = Covid-19 Burden. \\\\textit{N} = 179. * \\\\textit{p} < .05. ** \\\\textit{p} < .01. *** \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = F, # correctly print special characters
             threeparttable = T) # line breaks in the footnote

>>>>

@@

    # correlate variables
    correlations <- correlation_matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                                    "scs","ncs","dth","dtl","drf","covb")],
                                       type = "spearman",
                                       use = "lower",
                                       show_significance = FALSE,
                                       replace_diagonal = TRUE,
                                       replacement = "")

    # reorder the columns of the consistencies data frame to match the correlation columns
    consist_diag <- consistencies[c(colnames(correlations))]

    # create a vector of consistencies to be used as the diagonal in a table later
    consist_diag <- cbind(format(round(t(consist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
                          format(round(t(consist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))

    # paste together to create the output "alpha(omega)"
    consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")

    # add previously assembled diagonal with alpha and omega values
    diag(correlations) <- consist_diag

    # set row and column names for better table printing
    row.names(correlations) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","DTH","DTL","DRF","COV")
    colnames(correlations) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","DTH","DTL","DRF","COV")

    # create array with p-values of correlation coefficients
    corr_pvalues <- rcorr(as.matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                                 "scs","ncs","dth","dtl","drf","covb")]), type = "spearman")$P
    # replace upper triangle with NA
    corr_pvalues[upper.tri(corr_pvalues, diag = TRUE)] <- NA

@@

    # convert to matrix for the paste()-function
    correlations <- as.matrix(correlations)
    corr_pvalues <- as.matrix(corr_pvalues)

    # paste correlations and asterisks together
    correlations <- matrix(paste(correlations, corr_pvalues, sep = ""),
                           nrow = nrow(correlations), dimnames = dimnames(correlations))

@@

During visual inspection of correlation plots we noticed an unexpected outlier with very high MBI scores and very low NFC scores.
A Q-Q-plot contrasting Mahalanobis *D^2^* against expected Chi Square values confirmed the outlier.
To adhere to the preregistration, we report the results containing the outlier in this section and the results excluding the outlier in the **Supplementary Material**.

@@

  desc_table <-
  kbl(correlations,
      booktabs = T, # no vertical lines
      escape = F, # correctly print special characters
      align = rep("l",11)) %>% # right aligns the text in every column except for the first
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, COV = Covid-19 Burden. \\\\textit{N} = 180. * \\\\textit{p} < .05. ** \\\\textit{p} < .01. *** \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = F, # correctly print special characters
             threeparttable = T) # line breaks in the footnote
